Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-15 chi2012.tex
interaction description

Instances that cannot be dereferenced by a particular path selection  are left alone; an additional path selection can be created for such insances, which, like the first path selection, causes all appropriate instances to be dereferenced.  Each group can carry an arbitrary number of path selections, and each path selection can be extended arbitrarily deep by selecting successive properties of values. This achieves the ability to \emph{link slide} in the same way introduced by Parallax \cite{parallax}.

@@

>>>>

Instances that cannot be dereferenced by a particular path selection  are left alone; an additional path selection can be created for such insances, which, like the first path selection, causes all appropriate instances to be dereferenced.  Each group can carry an arbitrary number of path selections, and each path selection can be extended arbitrarily deep by selecting successive properties of values. This achieves the ability to \emph{link slide} as introduced by Parallax, but across sets of heterogeneous items by supporting multple parallel dereferenced paths simultaneously \cite{parallax}.

@@

\subsubsection{Coreference management: drag-and-drop sameas}

A major problem with data integration is consolidating representations that co-refer to the same entity, e.g. person, place or thing.  For example, effectively looking up properties of one's friends using Facebook and Google+ services, one might quickly want to combine the representations of our friends that have profiles on \emph{both} services to into single instances.

Although we considered a way to do this automatically, PS.2 revealed no way to reliably identify co-referring instances.  Thus,

To make this as easy as possible,

This was made \emph{optional}, so that people could opt to combine multiple representations co-referring to the same thing or not as it suits their purposes.  Keeping representations from multiple sources separate,
